\documentclass{article}
\usepackage[french]{babel}
\usepackage[T1]{fontenc}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{Star Wars World Secrets}
\usepackage{multicol}

\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
%\setmainfont[Mapping=tex-text]{Sitka Display}
\usepackage[small,sf,bf]{titlesec}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{sectsty}

\definecolor{DarkGreen}{HTML}{384d3e}
\definecolor{PureWhite}{HTML}{FFFFFF}
\definecolor{DarkRed}{HTML}{6e272d}
\definecolor{DarkGold}{HTML}{a48e3b}

\sectionfont{\color{DarkGreen}}
\subsectionfont{\color{DarkRed}}
\subsubsectionfont{\color{DarkGold}}

\begin{document}

\title{\vspace{-0.5cm}{\Huge Star Wars World Secrets} \vspace{-1cm}}

\date{}

\maketitle

\section*{1 --- 10 : Corporate}
\begin{enumerate}
	\item A new biotech firm is being established on the planet and plans to take advantage of local natural resources in its products. People are unaware that is has the backing of one of the richest individuals in the galaxy. That person is staking a large portion of their wealth on this firm’s success.
	\item The planet is about to become the new destination planet for high tech firms in the sector. The location, available land, natural resources, local populace, and governmental provisions all support the growth of businesses. They are about to become the 'Silicon Valley’ of the sector.
	\item A major corporation that operates on this planet is about to go belly-up. Whether it is through mismanagement or foul play is unknown, but the loss of jobs and production will cause a chain reaction that has a devastating impact on local economy.
	\item A new weapon of mass destruction is being privately developed by a relatively unknown tech firm. All knowledge surrounding the construction of this new weapon is heavily guarded. The company is not above eliminating possible loose ends that jeopardize the product.
	\item The shady corporate underbelly is alive and well on this planet. Major corporations are nearly required to maintain covert operatives, and even a covert military, that operate under the radar just to survive. Corporate business on this planet is both cutthroat and discreet. The cost is high but the rewards are even higher.
	\item The planet has a stigma of being a 'no-win’ planet for major corporations. All major corporations that have tried to develop business and profit on the planet have failed. In fact, most of them fail in an amazingly short amount of time. Some blame local saboteurs, some blame policies that don’t favor corporations, and some blame just plain old bad luck.
	\item A mega-corporation actually runs this planet. Although it has a traditional government, the corporation has enough pull and key players in strategic places that it essentially has near total control. Going against the corporation is the same as going against the local government.
	\item On this planet, there are several corporations that institute “blood oaths” after one has reached a certain level. It is akin to pledging one’s life to the corporation. This fact is relatively unknown until one reaches that level. Many view these corporations as having an extremely loyal command staff. This is the reason why.
	\item There is a corporation here that is a cover-up for the Imperials. It provides genuine services and goods, but its real purpose is to enable the Imperials to spy, transport goods and personnel, and capture important targets on the planet. The Imperials also use corporate takeovers to acquire land that locals wouldn’t have otherwise allowed them to get.
	\item There is a corporation here that is a Rebel sympathizer. The facility manufactures goods that it funnels to the Rebellion. They walk a very fine line between being a legitimate company and supporting the cause. If this fact was discovered, they could easily be shut down and many of the personnel would face Imperial punishment.
\end{enumerate}
\section*{11 --- 20 : Criminal}
\begin{enumerate}
	\setcounter{enumi}{10}
	\item Two criminal organizations are fighting for primary control of the planet. Many of the major crimes, assassinations, espionage, and major property damage, are related to the struggle for turf control between these two factions.
	\item A small-time Hutt has relocated to this planet and is looking to establish a name for himself as a major player in the sector.
	\item The criminal element of this society completely controls one major area on the planet (i.e. Sports, media, mass transportation, music, gambling, etc.).
	\item Although illegal drug use is relatively low on this planet, production of illegal drugs, such as spice, is incredibly high. The mass production of these drugs began relatively recently, so the planet isn’t known as a production planet yet. If current trends continue though, it won’t take long for that secret to become public knowledge.
	\item A major criminal element in this society (i.e. Gang, crime lord, pirates, etc.) are in partnership with an element of the local government. The two work together to accomplish goals that are mutually beneficial. If discovered, this would be disastrous for that element of government.
	\item The criminal element of this planet controls law enforcement. Most people view the law enforcement of the planet as lax or ineffective. But in reality, they have been corrupted at the highest levels and are at the whim of major criminals.
	\item Major criminal groups (i.e. Crime lords, large gangs, prolific pirates, etc.) do not last long on this planet. Low levels of crime definitely exist, but large criminal organizations never seem to be able to take hold in the region. They are always destroyed, dismantled, or seem to leave the area not long after arriving. No one has yet figured out an exact cause of why.
	\item Criminals on this planet follow a “Criminal Code” against one another while they operate on this planet. It is unknown where it originated, but most criminals will not commit criminal activity against another criminal while here. For those that break the code, the penalty is often death. It is rumored that a mysterious criminal organization even enforces this code.
	\item On this planet, there exists an actual school for criminals. It is secretive and invite only, but accepted students are taught in the ways of the hyper-criminal. They learn how to escape from law enforcement, defeat powerful security measures, infiltrate the upper-echelons of government, and overall become a successful career criminal.
	\item Two very influential criminal organizations recently left the planet for unknown reasons. The planet is now enjoying a resurgence with the lowest levels of crime it has seen in a long period of time. Many wonder what caused the criminals to leave and how long they will be able to enjoy this new prosperity.\end{enumerate}
\section*{21 --- 30 : Force}
\begin{enumerate}
	\setcounter{enumi}{20}
	\item An ancient Jedi temple has yet to be rediscovered on this planet. It has been undisturbed for hundreds, if not thousands of years.
	\item Many Force sensitive individuals have always considered this planet cursed due to how it “feels” in the Force. The truth is, a Sith Lord and his apprentice are imprisoned there in hibernation. Their power is so great, that their very presence casts a dark shadow upon the planet.
	\item A small monastery of Jedi monks inhabits a remote location on the planet. They generally are autonomous and keep to themselves, but are friendly and welcoming to outsiders. They have perfected the art of mind-wiping to keep their existence a secret.
	\item A cache of Jedi holocrons is hidden on the planet. Its existence almost falls into the realm of legend, but it does exist. There are many rumors about its actual location, but it has yet to be rediscovered.
	\item An oracle of significant power resides on this planet. Although most consider her a mythical story, she does actually exist. She has the ability to see into the future using her finally attuned Force powers. She is so specialized with her powers though, that she has almost no other Force powers that are not related to her oracle abilities.
	\item Force) Jedi on this planet often find their Force powers to be unreliable. It is unknown why, but the Force energy of this planet is distorted and causes Jedi difficulty with using their powers. Since Jedi are fairly rare in this part of the Galaxy, the fact isn’t commonly known.
	\item Many Jedi are unwittingly drawn to this planet. Very few understand or can explain why, other than to say existing on the planet feels “tranquil”. That tranquility appears to come with a cost though, as many Jedi are said to wander into the wilderness and never be seen from again.
	\item It is not uncommon for individuals that are not Force sensitive to manifest low-level Force-like abilities while on this planet. A small number have even left the planet and retained these abilities (typically those that live on the planet for an extended period of time). It is unknown why this sometimes happens.
	\item This planet is slowly toxic to Force users. Many Force users describe feeling that the longer they stay on the planet, the more “drained” they feel. Their Force powers become weaker and their connection with the Force becomes weaker. It is unknown why.
	\item An incredible battle between the Dark and Light side occurred in a specific area on this planet thousands of years ago. Any Force powers in this area have radically altered effects. Use of Force powers in the area is completely unsafe and unpredictable. There are some lost records that are still undiscovered on the planet of this legendary battle.
\end{enumerate}
\section*{31 --- 40 : Government}
\begin{enumerate}
	\setcounter{enumi}{30}
	\item The government of this planet, perhaps a Democracy (or similar group-run entity), is actually an elaborate front. The actual control of the entire planet rests on one specific individual who controls the government like a puppet.
	\item There is a small but powerful portion of the government that secretly supports a radical new direction for the planet. They are currently maneuvering to make the changes necessary for that to happen.
	\item The planetary government is involved in a major cover-up of galactic proportions (i.e. Illegal toxic waste disposal, hording life-saving technology, holding major galactic figureheads as prisoners, etc.). If discovered, the reputation and status of the planet would be ruined.
	\item The ruling body on the planet is one-step away from being destroyed. The planet will soon have no true form of government and will temporarily dissolve into a state of anarchy until a new form of government asserts itself.
	\item The local government has built an extensive network of secret bunkers in case of a planetary attack. Even though they may not appear to be, they are incredibly suited to withstand a large scale assault. They have bunkers throughout the planet for major government figures and even a small portion of the population.
	\item A network of disguised government buildings dots the urban landscape. These buildings are discreetly labeled and utterly forgettable. They house the intelligence, high-ranking military, and other top secrets of the government.
	\item All major leaders of the government are descended from the same family. This is not common knowledge and they use false information to spread the idea that this is not the case. But no one that is not from this particular family can ever hold an important government position on the planet.
	\item The local government has secretly made a pact with a major power in the Galaxy (i.e. The Empire, The Rebellion, a major crime lord or crime syndicate, etc.). The leaders have essentially sold their souls to this faction. To the outside observer, the planet is enjoying prosperity. To the insider, it will eventually be time to pay the piper.
	\item A secret organization, similar to the Illuminati, is rumored to run the planet. No one knows the members of this, but it is said that they are the true rulers of society. Often, strange coincidences that occur in public (i.e. Untimely death of a politician, unpopular laws enacted, etc.) are often attributed to this mysterious and masterminding organization.
	\item The government of this planet seems to change very frequently for no specific reason. In recent generations, it has been a monarchy, a democracy, a theocratic colony, and even warring federated tribes. The only thing certain about this planet’s government is uncertainty.
\end{enumerate}
\section*{41 --- 50 : Imperial}
\begin{enumerate}
	\setcounter{enumi}{40}
	\item A high-level Imperial prison is secretly located on this planet. It houses many enemies of the Empire that are thought to be dead or have gone missing. This would be a high value target of the Rebellion if they knew it actually existed.
	\item A training facility for elite Storm Troopers is being developed. Although it is not functional yet, Imperial presence has ramped up in the sector and locals are attempting to speculate why.
	\item Imperial Intelligence has identified this planet to be of “significant strategic importance” due to some factor. It could be its physical location, natural resources, local populace, or a variety of factors. They are actively looking to place a substantial Imperial presence on the planet.
	\item Numerous high-profile witnesses have been relocated to this planet as part of the Imperial Intelligence’s witness protection program. A breach in the security of this network could expose numerous valuable informants.
	\item This planet is considered a “cake” assignment for the Imperial military. Most hard-charging new recruits bid away from this planet, while older veterans looking for an easy assignment prior to retirement come here. The local Moff is not happy with that current designation and is looking to change that.
	\item Although it is not openly supportive of Imperial government, the local populace is in favor of being under Imperial rule. The average citizen believes that being under Imperial rule will mean an improvement in their lifestyle. Most support anything pro-Imperial and go against anything that contradicts that.
	\item The Imperials generally avoid this planet and very few people know why. Some attribute it to common practice (“We never land our troops there.”) while others claim a Moff secretly protects the planet from his own people. Either way, Imperial presence on the planet and in orbit is virtually nil.
	\item The Imperial military operates a base on one area of the planet that has no apparent purpose. It doesn’t guard anything. It has no mission. For all intents and purposes, there doesn’t need to be a base there but there is. Even the average soldier in the Imperial military has no idea why there is a base there or why they are stationed there.
	\item The Imperial military has slowly been stockpiling goods and equipment at hidden locations in the area. They are either planning to invade this planet, or an area near it. When they do, they will be well-prepared for a long siege.
	\item There is a large faction of Imperials located on this planet that are planning a coup of Imperials in the sector. They plan to secede from the Imperial military and take all of their equipment with them. This will mostly likely cause a larger conflict to escalate with the Imperial military as they send in more troops to reclaim what was theirs and destroy the deserters.
\end{enumerate}
\section*{51 --- 60 : Natural}
\begin{enumerate}
	\setcounter{enumi}{50}
	\item The core of the planet has been undergoing a series of chain reactions that will eventually destroy it. Natural disasters such as earthquakes, tsunamis and volcanic eruptions are becoming more common. The end of this planet is imminent if something doesn’t happen to reverse the changes that are occurring.
	\item An abundant natural resource of the planet is about to be eradicated due to a disaster (i.e. Lumber is destroyed by a rapidly expanding pest problem, drinking water is rendered unusable due to an accident or pollution, animal food supply decimated due to disease, etc.).
	\item A new natural resource (i.e. Fuel source, underground mineral, food stock, etc.) has recently been discovered on the planet. Originally thought to be a small boon to the local economy, it will turn out that this resource is found in abundance throughout the planet and will become a modern day gold rush.
	\item A local aboriginal species has yet to be discovered. They have been hidden in a remote area (i.e. Heavy jungle, subterranean caves, underwater, etc.) for centuries. If discovered, they would make an easy target for slavers due to their low level of technology.
	\item The planet is at the tipping point of a major ecological change. The primary terrain of the planet is about to become drastically different (i.e. Arctic to desert, rolling hills to large gorges and crevasses, tropical jungles to swampy sinkholes, etc.).
	\item A new use for an abundant natural resource has been discovered. This will be a boon for the economy as it will further drive up the value of the resource. But it will also cause other complications related to excessive extracting of the material. Depending on the material type, it may dry up from overconsumption.
	\item The planet hosts a unique and deadly virus. The indigenous population is immune to it and it is difficult to carry off planet. But if the right circumstances were met and it made it to another planet, the results would be catastrophic.
	\item Toxic waste pools and radioactive wastelands used to be commonplace on this planet generations ago. Scientists have recently discovered that the planet is naturally purging itself of these toxins that should like thousands of years. They have not yet discovered how.
	\item There are large crater fields on this planet that most assumed were created from meteorites striking the planet. However, no meteor fragments have ever been discovered. Most scientists believe that ancient people dug up the pieces and hauled them off or sold them. Others believe there is another explanation for these large crater fields.
	\item Large glaciers form at both poles (North and South) of this planet. The air space over both glaciers is considered a no-fly zone by pilots. Not because it breaks any laws, but because numerous aircraft and starships have been lost over both areas. It is unknown where these ships are lost or what causes them to disappear.
\end{enumerate}
\section*{61 --- 70 : Rebel}
\begin{enumerate}
	\setcounter{enumi}{60}
	\item There is a hidden Rebel base located on the planet surface. It is small, but houses vital information that cannot fall into enemy hands. It has existed for a relatively long period of time and has numerous assets.
	\item The Rebels have deemed this planet to be inconsequential to their goals. Although it has been viewed as a Rebel stronghold in the past, they are methodically moving their assets to another planet in the sector. Their eventual plan is to abandon the planet.
	\item The Rebellion uses the high orbit area of this planet as a get-away point. They have placed numerous signal disruptors, booby traps, and hiding spots throughout the area. It is well-known to their personnel that if they can flee to this area from the enemy, they have a great shot at using these resources and escaping.
	\item Rebel High Command has several key figures that reside in a single city on this planet. They are entrenched in the local populace but have a significant impact on decisions for the Alliance. If discovered, it would be a major blow against the Rebellion.
	\item This planet contains one of the few secret Rebel prisons. It is located outside of a popular urban area in a remote area (i.e. Island, large forest, underground, etc.). The Rebellion tries to minimize its footprint on the planet, but does have significant resources here due to the prison.
	\item The Rebels have a secret underground network that allows them to hide high value targets here. The network uses sympathizers, secret hiding locations, underground transport, and numerous other components to safely make their valuable assets disappear.
	\item The Rebellion has no presence on this planet. In fact, they are surprisingly absent from a planet, which for all intents and purposes, looks to be ideal for their strategic needs.
	\item There is a significant spy support network on this planet that is loyal to the Rebel Alliance. Although they don’t all work under the Rebellion, per se, many are loyal to the Rebellion and believe that the interests of the Rebels align with their own.
	\item The Rebel forces on this planet have been incurring heavy losses recently. What they don’t know is that they have been severely infiltrated by Imperial spies. Their destruction on this planet and in this sector is inevitable, unless someone discovers the infiltration.
	\item The planetary inhabitants recently became very unfriendly to Rebel forces. So much so, that the Rebellion is having to decide whether they will withdraw from the area or attempt to take the planet by force. It is unknown why this seemingly Rebel-friendly planet turned hostile.
\end{enumerate}
\section*{71 --- 80 : Religious}
\begin{enumerate}
	\setcounter{enumi}{70}
	\item A fanatical and cult-like off-shoot of a local planetary religion is gaining steam within the populace. They are responsible for numerous criminal acts and their violence seems to be increasing drastically.
	\item The prominent figurehead of a local religion is a fraud. She has adeptly led her followers to believe that she is the “Chosen One” but has only her own interests at heart. She is planning something diabolical (i.e. Mass suicide, theft of all religious gifts, overthrowing the local government, etc.).
	\item Nearly 100\% of local natives are disciples of a local religion. They have decided that the only way to expand their religion is to begin off-planet pilgrimages. They are currently in the planning phase of this endeavor.
	\item An ancient religion was wiped out long ago, but its teachings and history have been preserved and are waiting to be discovered. It contains some secret that will change things in the area (i.e. Answers to a local mystery, the key to stopping a local war, a unique connection to the Force, etc.).
	\item The primary local religion secretly employs some taboo practice (i.e. Humanoid sacrifice, cannibalism, Force voodoo, etc.). They understand their practices are taboo to others and work extremely hard to keep those practices a secret.
	\item Not long ago, a significant portion of a local religion began a sacred pilgrimage into the wilderness. They numbered into the tens of thousands (or more, if appropriate). The pilgrims disappeared without a trace. Most of the few remaining members of the religion have left it and it has all but disintegrated.
	\item A new religion seems to have spawned from out of nowhere. It is rapidly moving through the local population and is quickly gaining significance. The rate at which it is converting believers is astonishing. The growth is unlike anything seen elsewhere in the galaxy.
	\item Every ten years, the leader and figurehead of a local religion disappears. The next in command takes his place, to lead his people and be treated like a god, only to disappear after ten years. This cycle is commonly accepted by its followers but less so by outsiders. No one knows where the leader disappears to or what happens to them. Most assume death.
	\item A new race of aliens has been arriving on the planet in droves. They are generally peaceful, but have proclaimed this planet their sacred homeland. Their presence is causing strife in the local population. The alien race is not known to have any historical presence here.
	\item Religion is absent on this planet. The local inhabitants are against all forms of open worship, churches, open religious ideology, and generally anything religious. This disdain for religion has been a long-standing issue on the planet that few know the origin of.
\end{enumerate}
\section*{81 --- 90 : Tech}
\begin{enumerate}
	\setcounter{enumi}{80}
	\item A self-automated droid manufacturing facility exists in a subterranean compound. It is completely autonomous, mining its own resources, manufacturing droids and expanding its own domain. Its origins and purpose are a complete mystery.
	\item A large satellite array that orbits the planet is commonly thought to be the primary source of communication and weather data for the inhabitants. Its true nature, however, is as a remarkable spy network that is able to provide surveillance on the entire planet. But for who?
	\item There is a disguised communication network with incredible redundancy on the planet. It is nearly impossible to knock out or jam planetary communications. The network is a combination of old alien technology that locals merged with new technology.
	\item The planet has a substantial planetary defense grid that consists of missile silos and Planet Defenders (heavy ion surface-to-space cannons). Although it isn’t advertised by the local military, the planet is well setup to defend against planetary bombardment.
	\item There is a significant electric disturbance in the planet’s atmosphere that occasionally damages electrical equipment and even injures people. This fact is commonly known. However, scientists have determined that it is not a natural function, but other than that they do not know the cause.
	\item Non-sentient droids on this planet have been known to spontaneously become sentient. It is rare and no one knows why, but it has happened enough to where locals have deemed it an actual phenomena.
	\item There is an abandoned cloning facility that is located in an area rarely frequented on the planet. Many centuries ago it was used to fight wars in the distant past. It has since become a lost relic that is yet to be rediscovered.
	\item Large, unmanned platforms float in the ocean and process both the water and air of the planet into a habitable environment. No one knows who initially installed these terraforming devices many generations ago. Also, no one knows how long these unmanned processing stations will continue to operate and maintain the planet’s habitat.
	\item There is a local “species” of droid that inhabits the planet. They have inhabited the planet for a long time. No one knows of their origin. Even they claim ignorance of how their people originated. However, they function on this planet much like any other native race does so on their home planet. They are never encountered off-planet though and have no desire to leave.
	\item There is a unique type of technology that only exists on this planet. It is used to power many local vehicles, such as speeders or ground vehicles. The technology will not function outside of the planet though. No one knows why, but some surmise there is something about the planet’s structure that allows the technology to function there (and there only).
\end{enumerate}
\section*{91 --- 101 : Unusual}
\begin{enumerate}
	\setcounter{enumi}{90}
	\item A clan of assassins has existed and trained on this planet for thousands of years. Although their existence is not a mystery, the fact that they originate from this planet is.
	\item An ancient “elevator” exists that drills down nearly to the core of the planet. It is huge, several kilometers in diameter. No one knows who built it or what its purpose was. Local government has deemed it off-limits and it is heavily guarded by the local military.
	\item During a predictable time period (i.e. One week, three months, yearly, etc.), a large pulse of energy emanates from the planet. No one knows if it is man-made or natural. Precautions must be taken to not be injured or items damaged by this energy.
	\item The planet, for lack of a better term, is haunted. Many people believe large crystals on the planet have something to do with keeping the spirits of the dead around. But no one truly knows for sure. Residents of the planet accept the haunting as commonplace.
	\item There is a small populace of a “species” on this planet that most consider to be “undead”. They have a primitive cognitive thought process and are only interested in basic primal needs. They are incredibly homicidal and almost animal-like. They are often referred to as, galactic zombies. No one understands their biology or knows their true origins.
	\item Large humanoid statues of an unknown race dot the landscape of this planet. No one knows the origins of these statues, but many surmise they are statues of the ancient ancestors of this planet. The statues have been known to periodically change locations throughout the centuries. No one knows how or why they move.
	\item There is an abandoned colony on the planet that few know about. The natives of the colony are not of the same species as the other inhabitants of the planet. They have lived and operated in their secluded environment for several generations.
	\item There is a unique type of rock on this planet that is capable of storing the memories of organic beings. Some say intense emotion or even the Force is required to imprint these memories on the rocks, but no one truly knows the process. Scientists are still developing and perfecting a process for retrieving these memories for “historical purposes”.
	\item A race of aquatic people inhabit the deep oceans of the planet. They keep their distance from all surface dwellers and little is known about them. All efforts to make contact with them have met with swift and decisive force. In general, most of the general population has a, “Leave them be if they leave us be,” attitude towards the situation.
	\item This planet is not the typical ball of substance orbiting a star. The core is a mechanical space station thousands of years old. The exterior of the station was terraformed over and an atmosphere was established. No one knows who accomplished this great feat of construction.
	\item All the inhabitants of this planet mysteriously disappeared about a thousand years ago. The planet was subsequently looted and repopulated after a brief period of war for control of the planet. But no one has ever discovered what happened to the millions of people that inhabited the planet and disappeared over night.
\end{enumerate}
\end{document}
