\documentclass{article}
\usepackage[french]{babel}
\usepackage[T1]{fontenc}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{One Roll Spaceships}
\usepackage{multicol}

\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
%\setmainfont[Mapping=tex-text]{Sitka Display}
\usepackage[small,sf,bf]{titlesec}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{sectsty}

\definecolor{DarkGreen}{HTML}{384d3e}
\definecolor{PureWhite}{HTML}{FFFFFF}
\definecolor{DarkRed}{HTML}{6e272d}
\definecolor{DarkGold}{HTML}{a48e3b}

\sectionfont{\color{DarkGreen}}
\subsectionfont{\color{DarkRed}}
\subsubsectionfont{\color{DarkGold}}

\begin{document}

\title{\vspace{-0.5cm}{\Huge One Roll Spaceships} \vspace{-1cm}}

\date{}

\maketitle

\section*{D4 : How large is it?}
As mentioned before, all ships are relatively small. Think the Millenium Falcon or Serenity.
\begin{enumerate}
	\item Smaller than normal. (-2 HUL, fast)
	\item As large as normal.
	\item Larger than normal. (+4 HP, +2 HUL, slow)
	\item Much larger than normal. (+8 HP, +4 HUL, very slow)
\end{enumerate}

\section*{D6 : What kind of ship is it?}
Note that this is only its intended design, not necessarily what it is currently being used for.
\begin{enumerate}
	\item Military: For combat or troop/starfighter transport. (+1 Armour/+1 damage)
	\item Research: For exploration, survey, and analysis. (laboratory, medbay)
	\item Industrial: For mining, construction, salvaging, etc. (various tools)
	\item Merchant: For transporting goods and resources. (huge cargo bay)
	\item Liner: For transporting many individuals at once. (many cryopods)
	\item Personal: For transporting a few individuals in luxury. (many staterooms)	
\end{enumerate}

\section*{D8 : Who owns and operates the ship?}
This determines what sorts of jobs it performs, who crews it, and what sort of legal recourse attacking (or helping) it incurs.
\begin{enumerate}
	\item A major interstellar power.
	\item Rebels, rogues, and dissidents.
	\item A private individual living aboard the ship.
	\item Independent workers who own their own ship.
	\item A megacorporation.
	\item Friendly or neutral aliens.
	\item Hostile or enigmatic aliens.
	\item Robots, independent or for their owners.
\end{enumerate}

\section*{D10 : What is its main strength?}
Most of these are combat related, but can also say something about what it is used for, either beyond its initial design or what specific role within that design.
\begin{enumerate}
	\item Reinforced hull. +3 HUL.
	\item Large engines. +3 ENG.
	\item Overclocked systems. +3 SYS.
	\item Armour plating. +1 Armour.
	\item Targeting computers. +1 damage.
	\item Strong shields. +4 HP.
	\item Exceptional maneuverability.
	\item Long range, high accuracy sensors.
	\item Difficult to detect and scan.
	\item Has the benefits of another ship type.
\end{enumerate}

\section*{D10 : What is its main weakness?}
As above, but in reverse, saying what it isn't used for. Can also be useful to determine what went wrong on a damaged or derelict ship.
\begin{enumerate}
	\item Cracked hull. -3 HUL.
	\item Small engines. -3 ENG.
	\item Buggy systems. -3 SYS.
	\item Obvious weak points. HUL damage always causes critical damage.
	\item Undersized weapons. -1 damage.
	\item Weak shields. -4 HP.
	\item Slow turns and acceleration/deceleration.
	\item Inaccurate, obvious sensors.
	\item Adware constantly broadcasts its position.
	\item Lacks the benefits of its ship type.
\end{enumerate}

\section*{D12 : What is it doing?}
Vague, but keeping in mind the previous rolls can help narrow down exactly what it's doing.
\begin{enumerate}
	\item It's a pirate ship, and pursues the party. +1 damage if not a Military ship.
	\item It's a pirate ship, and is pursuing/boarding a ship. +1 damage if not a Military ship.
	\item It's being hunted by, or is hunting, a pirate ship.
	\item It's drifting in space, somehow damaged or disabled and in need of aid.
	\item It's following the party, purely by coincidence.
	\item It's defending something, and threatens the party against approaching it.
	\item It's doing whatever it is it was built to do, but is obviously about to fail.
	\item It's offering the party a trade, but rarely one as simple as credits for fuel.
	\item It's doing whatever it is it was built to do, but in a way dangerous to the party.
	\item It's resupplying from a cache of valuable materials, and is clearly vulnerable.
	\item It's requesting the party's aid in return for a reward.
	\item It's offering the party something its crew has no use of, but they would appreciate.
\end{enumerate}

\section*{D20 : What does it look like?}
Again this is mostly for flavour, but again it can also be a good base for coming up with ideas. A corporate ship that's blocky and grey will be run by a very different corporation, ro at least for very different purposes, than one that looks sleek and elegant.
\begin{enumerate}
	\item Blocky and grey, totally devoid of intentional aesthetic.
	\item Sleek and elegant, pure white with black glass.
	\item Black and angular, as if a stealth ship.
	\item Green and organic-looking – possibly a living ship.
	\item Red and curved, like a retrofuturist rocket ship.
	\item A mechanical cube, sphere, pyramid, or other polyhedron.
	\item Spindly and elegant, golden and shimmering with large glass planes.
	\item A Frankenstein of several other ships welded together.
	\item Dark blue, long and with rounded edges and bright yellow windows.
	\item Ostentatious and religious, like a cathedral turned into a ship.
	\item Bright white plastic with blue and orange extremeties.
	\item A series of bright green spheres connected by pipes.
	\item Insectoid in appearance, with bright, clashing colours.
	\item Cartoonish, covered in stars, constantly shifting between several vibrant colours.
	\item Narrow and angular, like an upsized starfighter.
	\item Round, smooth edges, dull yellow, orange, or brown.
	\item Imposing, blocky, and long, red as blood.
	\item White, sleek exterior half-conceals a pitch black, biomechanical interior.
	\item An asteroid, space station, or even space lifeform's corpse turned into a ship.
	\item Deep purple, with shiny metallic trimming.
\end{enumerate}

\end{document}
