\documentclass{article}
\usepackage[french]{babel}
\usepackage[T1]{fontenc}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{One Roll Bounty Hunter}
\usepackage{multicol}

\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
%\setmainfont[Mapping=tex-text]{Sitka Display}
\usepackage[small,sf,bf]{titlesec}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{sectsty}

\definecolor{DarkGreen}{HTML}{384d3e}
\definecolor{PureWhite}{HTML}{FFFFFF}
\definecolor{DarkRed}{HTML}{6e272d}
\definecolor{DarkGold}{HTML}{a48e3b}

\sectionfont{\color{DarkGreen}}
\subsectionfont{\color{DarkRed}}
\subsubsectionfont{\color{DarkGold}}

\begin{document}

\title{\vspace{-0.5cm}{\Huge One Roll Bounty Hunter} \vspace{-1cm}}

\date{}

\maketitle

\section*{D4 : Who are they hunting?}
This is pretty self-explanatory, but I would recommend you let the party know who's being hunted and why - just not who by or when they'll strike.
\begin{enumerate}
	\item A member of the party.
	\item A close ally of the party.
	\item Someone temporarily critical to the party's goals.
	\item An enemy of the party. They'll fight anyone who tries to kill them instead.
\end{enumerate}

\section*{D6 : What is their demeanour?}
This comes up most when the bounty hunter is monologuing to seemingly defeated prey, but can also say something about how they fight. Mostly it's just for flavour.
\begin{enumerate}
	\item All business, no nonsense.
	\item Extreme aggression, easily provoked.
	\item Boring and plain.
	\item Cheerful, bordering on saccharine.
	\item Melancholic and fatalist.
	\item Showy and narcissistic.
\end{enumerate}

\section*{D8 : What's their modus operandi?}
Again, pretty self-explanatory. They're broad descriptions, however, so you have plenty of room to determine exactly what kind of explosive, vehicle, etc they're using.
\begin{enumerate}
	\item Explosives and heavy weapons.
	\item Long range weapons, sniping.
	\item Automated drones.
	\item Stealth and melee weapons.
	\item Hired help.
	\item Heavy armour and close range weapons.
	\item Combat vehicles.
	\item All-rounder weapons and gear.
\end{enumerate}

\section*{D10 : What specialist gear do they own?}
It can be daunting to combine two seemingly incompatible methods and specialist gears, but think on how they could work together. A sniper in power armour, for example, could wield much larger weapons, or stand straight out in the open without fear of easy retaliation.
\begin{enumerate}
	\item A jetpack, reliable but easily damaged.
	\item Ancient weaponry that ignores armour.
	\item A heavily upgraded, combat-specialized starship.
	\item Power armour and energy shields.
	\item Combat drugs.
	\item High tech tracking and scanning devices.
	\item A cloaking field.
	\item A bioengineered combat/tracking pet.
	\item Nanotech weapons, easily concealed.
	\item Multiple cybernetic augmentations.
\end{enumerate}

\section*{D10 : What do they look like?}
Another flavour roll, but think about how their appearance combines with their tactics and gimmick - for example, someone wearing corporate-branded punk gear tells a story.
\begin{enumerate}
	\item Nondescript, easily blending into crowds.
	\item Military surplus everything, trying a little too hard.
	\item Elegant and elaborate clothes and gear, like a fashionista.
	\item Practical equipment, worn by years of use.
	\item Punk fashion with tons of accessories.
	\item One colour all over, lots of fabric and plastic.
	\item Robes and masks, mystical in nature.
	\item Revealing clothes, covered in tattoos and cosmetic implants.
	\item Stylish clothes, suits and ties, dark and sleek.
	\item Brand new everything, most of it never used before.
\end{enumerate}

\section*{D12 : What species are they?}
In some cases, species is little more than another flavour roll, but a clever bounty hunter (IE all of them) will know how to use their biology to their advantage. Vatborn, Mentats, and Spacers are all "panhumans", human but somewhat different from the baseline.
\begin{enumerate}
	\item Human, +2 to their lowest stat.
	\item Vatborn, +2 STR.
	\item Mentat, +2 CHA.
	\item Spacer, +2 DEX.
	\item Lizard, +1 DEX and immune to heat.
	\item Feline, always acts before enemies/traps.
	\item Hound, preternatural sense of smell.
	\item Mantis, D8 unarmed damage.
	\item Rabbit, outrun anyone, even some vehicles.
	\item Yeti, +1 STR and immune to cold.
	\item Assassin Robot, closely resembles an organic.
	\item Combat Robot, +1 Armour at all times.
\end{enumerate}


\section*{D20 : What's their gimmick?}
Every self-respecting bounty hunter has something that sets them apart from the crowd, either as a marketing technique or a quirk picked after years of stressful work.
\begin{enumerate}
	\item They warn all their targets in advance.
	\item There's two of them: twins, friends, lovers, clones, etc.
	\item They're actually several people working in turns. Kill one and another comes back.
	\item They take great care to avoid any collateral damage.
	\item They try to make each kill slow and painful.
	\item They have branded corporate gear and try to show it off.
	\item They're exceptionally young or old, but no less effective for it.
	\item They offer to fake the party's deaths in return for a bribe.
	\item They carry incendiary grenades and are a pyromaniac.
	\item They have limited psychic ability. One power, always the CHA drawback.
	\item They are followed by a documentary crew.
	\item Their will places a large bounty on whoever kills them, larger than any existing ones.
	\item They are being hunted by another bounty hunter themselves.
	\item They dual wield their weapons. It looks cool but provides no benefit.
	\item They use only sidearms, daggers, and other "light" weapons and gear.
	\item They revel in causing unnecessary collateral damage.
	\item They are exceptionally skilled: +2 HP and +1 damage.
	\item They are particularly inept: -2 HP and -1 damage.
	\item They throw sonic devices which emit loud, piercing screeches they are immune to.
	\item They talk to their quarry constantly throughout the fight.
\end{enumerate}

\end{document}
