\documentclass[twoside]{article}
\usepackage[french]{babel}
\usepackage[T1]{fontenc}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[LE]{\thepage}
\fancyfoot[RO]{\thepage}
\fancyfoot[C]{}
\usepackage{siunitx}
%\usepackage{anyfontsize}

\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
\setmainfont[Mapping=tex-text]{Sitka Display}
\usepackage[small,sf,bf]{titlesec}

\usepackage{graphicx}
\usepackage{xcolor, colortbl}
\usepackage{sectsty}

\definecolor{DarkGreen}{HTML}{384d3e}
\definecolor{PureWhite}{HTML}{FFFFFF}
\definecolor{DarkRed}{HTML}{6e272d}
\definecolor{DarkGold}{HTML}{a48e3b}

\sectionfont{\color{DarkGreen}}
\subsectionfont{\color{DarkRed}}
\subsubsectionfont{\color{DarkGold}}

\begin{document}


\title{\vspace{-0.5cm}{\Huge  Chroniques du gardien} \vspace{-1cm}}

\date{}
\maketitle


\section{L'héritage du gardien}
\subsection{How to introduce your characters}
Player Characters begin play on Spintir at the Dawn Temple.  The Jailor, after reviewing records and verifying that all of the prisoner inmates are accounted for, discovers a note in the Jedi Records detailing a Jedi who was scheduled to be taken to the Dawn Temple, who vanished before capture, and has never arrived fleeing before anyone knew what had happened.  The Jailor had previously dispatched known archeologist Hethan Romund to uncover this mystery and she has since vanished.\\

Hethan Romund hired the crew of the Silver Star in Reles and traveled offworld in search of this Siljo Warde last known to be on Eriadu.  Her travels, unknown to the PJs, lead her to Cato Nemodia where she came into possession of Siljo Warde's Holocron stumbling across the Holocron in the market thanks to Aenet one of the Silver Star's crew members.  Unfortunately the Silver Star's swift departure attrached the attention of Duke Irbain, who callously decided to have the crew killed on the suspicion of sedition.\\

The Jailor immediately insists that the PJs track down Hethan Romund and the mystery of Suljo Warde.  The Jedi Knight and Hethan's last known location was aboard the Silver Star.  They know Hethan Romund was headed to Eriadu but could have made several steps along the way.  If the PJs do not have a starship (Which one has not been awarded yet in the Force and Destiny Storyline) the PJs must take registered transport out of Reles on Spintir.  The PJs should be using their sensors to track down Hethan Romund's signal aboard the Silver Star.  This should open up he optional encounter: Finding the Holocron.  The PJs detect Hethan Romund's distress signal.\\

This is the reason and justification for why the PJs are on this adventure path.

\subsection{Ways to Expand the Adventure}
Throughout Chronicles of the Gatekeeper there is a sub plot about being in possession of a Holocron can be a dangerous outcome as there are many other parties interested in the history and lore of the Jedi.  A Game Master is allowed to post bonus encounters if they complete the session early allowing for such theme.\\

\textbf{Finding the Holocron}: One way to expand the adventure is for a Game Master to review the adventure logs for \textbf{Hidden Depths}.  If Iron Arm survived and is hunting the PJs perhaps he is the one who sent the Bounty Hunters after the Silver Star Freighter.  Iron Arm reports to Duke Erron Irbain an Imperial Official from Cato Neimoidia.  Iron Arm can be on Arboonie in place of the Stormtrooper Commander doing the Duke's work.\\

GMs discretion, Hethan Romund can be either (1) on the G9-Rigger known as the Silver Star Freighter and killed in the attack using her dying action to hint where the PJs who rescued them can locate the hidden holocron.  (2) Aenet, one of the Freighter's crew, stole the Holocron from Hethan Romund as a souvenir that reminders her of stories of the Jedi from her childhood.  In this case she left Hethan Romund behind on Cato Nemodia.  If Hethan Romund is left behind she can can either be (1) captured by Duke Irbain on Cato Nemodia and scheduled to be executed.  This can allow the PJs an opportunity to attempt to rescue her in Act 2.  Or, (2) a Game Master can decide that Hethan Romund has no real importance to the overall story and she got separated from the crew and is out of communication and finding her own way back to the Dawn Temple on Spintir.\\

\textbf{Destiny Calls}:  At the end of the Destiny Calls encounter, The BARON will contact the PJs in an effort to get an update on the fate of Hethan Romund.  He will ask if they found and clues.  Upon learning that the have in their possession a Jedi Holocron and that it has a lead to teach them the Force Power: Warde's Foresight, The BARON asks the PJs to make getting this information a top priority.  The BARON has a goal to restore the Baran Do Sage Order.  Warde's Foresight as a force power is essential to this mission being completed.\\

\textbf{Imperial Interference}:  If the GM chooses to use the optional encounter Imperial Interference the GM can edit this encounter to include Iron Arm.  Before a Game Master does so he should check player's adventure logs for \textbf{Hidden Depths} to verify the fare of Iron Arm.\\


\subsection{Récompenses de l'héritage du gardien}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{4cm}|p{12cm}|}
	\hline 
	\cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Élement de l'histoire}}} & \cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Récompense}}} \\ 
	\hline 
	La Résistance & Les PJ ont-ils rejoint la Résistance ?  Si oui, ont-ils trahi et livré la Résistance pour obtenir le Kyber Cristal de Suljo Ward ?  Les PJ ont-ils aidé la Résistance à renverser Marcolf ?  Si un joueur est également membre de l'Alliance Rebelle, le PJ a-t-il tenté de recruter la Résistance pour devenir une cellule de la Rébellion ?  Si c'est le cas, Alda Base gagne un groupe de sous-fifres de guerriers Sathari. \\ 
	\hline 
	1er cristal Kyber & Comment les joueurs ont-ils obtenu le premier Kyber Cristal de Suljo Warde ?  Le fait d'être en possession du Kyber Cristal débloque la première amélioration de contrôle et de force pour le pouvoir de Prévoyance de Warde.  Voir la Prévoyance de Warde aux pages 10-11 du module d'aventure. \\ 
	\hline 
	Conséquences pour Quolas & Qu'arrive-t-il à Quolas après le départ des PJ ? Voir page 39. \\ 
	\hline 
\end{tabular} 

\subsection{Récompenses d'XP}
\begin{tabular}{|p{12cm}|p{4cm}|}
	\hline 
	\cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{XP}}} & \cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Récompense}}} \\ 
	\hline 
	Tuer Marcolf ou le forcer à fuir Quolas. & 5 XP \\ 
	\hline 
	Retirer Marcolf du pouvoir sans le tuer pour qu'il puisse faire face à la justice pour ses crimes. & 10 XP \\ 
	\hline 
	Négocier une trêve entre les clans rivaux. & 10 XP \\
	\hline 
	Arrêter la profanation du Pilier des Ancêtres. & 5 XP \\
	\hline 
	Aider les citoyens de Quolas dans la section \textbf{Vivre dans la peur} (voir pages 27-33).	 & 1 -- 5 XP par citoyen aidé \\
	\hline 
	Éviter le lieutenant Devrays et ses troupes d'assaut ou traiter avec eux d'une manière qui n'entraîne pas de représailles impériales contre la ville. & 5 XP \\
	\hline 
	Bon jeu de rôle (jouer en fonction des obligations, des devoirs, de la moralité et des motivations du personnage) & 1 -- 5 XP \\
	\hline 
\end{tabular}


\section{La chasse aux fantômes}
\subsection{How to introduce your characters}
Players who have not complete Act 1 can be introduced by having the players return to the Dawn Temple on Spintirr after completing Act 1 and picking of new recruits recently brought to the temple through past roleplaying experiences or through new recruitment by members of the Church of the Force or The BARON.\\

In the second episode of Chronicles of the Gatekeeper, the Player Characters follow Warde's trail to the world of Cato Neimoidia.  It is highly recommended that players complete \textbf{Act 1: The Gatekeeper's Legacy} prior to completing Chasing Ghosts.  Game Masters should check the players Adventure Logs from The Gatekeeper's Legacy to see how the results of that adventure affect story elements in Act 2.\\

Furthermore, a Game Master should ask the players to describe their character, how they are dressed, and what weapons they are carrying with them.  How the PJs are dressed and what weapons they take and bring openly greatly affects how the locals of Jorra interact with the PJs.\\

Warde's Holocron, after the PJs install the kyber crystal obtained from Gel Marcolf in \textbf{Act 1 The Gatekeeper's Legacy}, discloses to the party that Warde received orders from the Jedi Council to interrupt his mission on Arboonie and that he was to travel to Cato Neimoidia to assist the Republic's efforts to take the important city of Jorra.\\

\subsection{Ways to Expand the Adventure}
Throughout Chronicles of the Gatekeeper there is a sub plot about being in possession of a Holocron can be a dangerous outcome as there are many other parties interested in the history and lore of the Jedi.  A Game Master is allowed to post bonus encounters if they complete the session early allowing for such theme.\\

\textbf{Fate of Hethan Romund:} If Hethan Romund was included in \textbf{Act 1: The Gatekeeper's Legacy} as the reason that started the PJs on this mission and was left behind she can can either be (1) captured by Duke Irbain on Cato Nemodia and scheduled to be executed.  Hethan Romund is being held at the Southside Prison.  Execution by the Empire will be carried out by having them NPJ fall from the heights of the City down into the mists below.  No one can survive such a fall. During the course of the adventure the PJs can learn about the fate of Hethan Romund during an encounter with Iron Arm or during the Reunion optional encounter if the PJs choose to help Sanna Olpan.  This can allow the PJs an opportunity to attempt to rescue her in Act 2. \\

\textbf{This Looks Suspicious}: Optional Encounter.  In this optional encounter the Game Master should reference the players adventure logs from \textbf{Act 1: The Gatekeeper's Legacy} and \textbf{Hidden Depths}.  This will inform the GM of the current status of Iron Arm a recurring nemesis in Season 1 of the Force and Destiny story of Legends of the Galaxy.  If the PJs bring a holocron, including Warde's Holocron, or a lightsaber with them and it is discovered during a search.  Iron Arm is informed and he called to Jorra to investigate the PJs.  Iron Arm reports to Duke Erron Irbain an Imperial Official from Cato Neimoidia. \\

Furthermore, A GM should consider making this scene play out similar to what is seen in Solo: A Star Wars Story at the beginning of the Movie when Han and Qi'ra were trying to get through the checkpoint at the starport on Corellia.\\

\textbf{Welcoming Committee:} Optional Encounter.  In this optional encounter the Game Master the Game Master is encouraged to have a confrontation with the PJs and Iron Arm.  Any encounter with Iron Arm can result in the PJs learning that Hethan Romund is being held in the Southside Prison.  The PJs should be encouraged to stage a rescue attempt for their mentor.  However, this is an optional encounter.  The GM should note the fate of Hethan Romund.\\

\textbf{Rescue of Hethan Romund:} If the PJs wish to rescue their former mentor Hethan Romund they must stage a rescue attempt by breaking into Southside Prison.  The GM should warn the PJs that in doing so they will bring allot of unwanted attention.  It is encouraged for the PJs to attempt this at the very end of the adventure to prevent it from disrupting their investigation into Suljo Warde.  When the PJs are rescuing Hethan Romund they may also attempt to rescue Sanna Olpan's son Gren.\\


\subsection{Récompenses de la chasse aux fantômes}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{4cm}|p{12cm}|}
	\hline 
	\cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Élement de l'histoire}}} & \cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Récompense}}} \\ 
	\hline 
	Guérison de vieilles blessures & Est-ce que les PJs ont eu des problèmes avec les locaux sur Jorra ? Ont-ils perdu du matériel ou attiré l'attention des criminels et des impériaux ?  Ont-ils écrit des fautes du passé ? Que pensent les habitants de Jorre des PJ à la fin de cette aventure. \\ 
	\hline 
	Questions et évasions & Qu'est-ce que les PJ ont appris sur Suljo Ward ? \\ 
	\hline 
	Destin de Hethan Romund & Les PJ ont-ils réussi à sauver Hethan Romund ? \\ 
	\hline 
\end{tabular} 

\subsection{Récompenses d'XP}
\begin{tabular}{|p{12cm}|p{4cm}|}
	\hline 
	\cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{XP}}} & \cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Récompense}}} \\ 
	\hline 
	Résolution des problèmes lors de la rencontre de Guérison des blessures. & 1 -- 5 XP \\ 
	\hline 
	Obtenir les informations nécessaires de Zel N'got sans le blesser, le tuer ou le menacer inutilement. & 5 XP \\ 
	\hline 
	Sauver Tor Haido des Crimson Kreehawks. & 5 XP \\
	\hline 
	Perturber ou démanteler le syndicat Whitescar ou formation d'une alliance avec Onrein Hasar. & 5 -- 10 XP \\
	\hline 
	Rencontrer le TH-313 sans exposer ses sympathies Jedi. & 5 XP \\
	\hline 
	S'occuper du chasseur de primes Dalan Oberos. & 10 XP \\
	\hline 
	Bon jeu de rôle (jouer en fonction des obligations, des devoirs, de la moralité et des motivations du personnage) & 1 -- 5 XP \\
	\hline 
\end{tabular}


\section{La fin des Chroniques}
\subsection{How to introduce your characters}
Players who have not complete Act 1 or Act 2 can be introduced by having the players return to the Dawn Temple on Spintirr after completing Act 3 and picking of new recruits recently brought to the temple through past roleplaying experiences or through new recruitment by members of the Church of the Force or The BARON.\\

In the third episode of Chronicles of the Gatekeeper, the Player Characters follow Warde's trail to the world of Moraband.  It is highly recommended that players complete \textbf{Act 1: The Gatekeeper's Legacy} \& \textbf{Act 2: Chasing Ghosts} prior to completing Chronicles' End.  Game Masters should check the players Adventure Logs from The Gatekeeper's Legacy to see how the results of that adventure affect story elements in Act 3.\\

Warde's Holocron, after the PJs install the kyber crystal obtained from Gel Marcolf in \textbf{Act 1 The Gatekeeper's Legacy}, discloses to the party that Warde received orders from the Jedi Council to interrupt his mission on Arboonie and that he was to travel to Cato Neimoidia to assist the Republic's efforts to take the important city of Jorra.\\

After installing the 2nd Kyber Crystal into Suljo Warde's holocron the Gatekeeper suggests the PJs travel to a watery moon in the Delriss system to find Moraband's coordinates in the archives of a forgotten Jedi Base.\\

\subsection{Ways to Expand the Adventure}
\textbf{Uninvited Company:} The PJs are not the only ones interested Warde's legacy.  One interested group followed them to Moraband.\\

If the PJs have not already defeated Onrein Hasar, she became aware of the PJs' quest to track Ward during \textbf{Act 2: Chasing Ghosts} she has followed them PJs with her two IG-100 MangaGuard bondygards and a trusted lieutenant Lor Kein.  For muscle she has brought  2 groups of 3 Kreehawk Gangers.\\

If the PJs did not already defeat the bounty hunters from \textbf{Act 1: The Gatekeeper's Legacy}.  Then Nex Pavros and the bounty hunters who survived their encounter plus 2 additional bounty hunters to back up the original 4 bounty hunters.  They fight the PJs with hopes at gaining revenge.\\

If Iron Arm has survived thus far he along with 2 Death troopers and 2 minion groups of 3 stormtroopers have arrived to arrest the PJs and bring them to justice.\\

If none of the PJs past rivals have shown up, then the GM is encouraged to have a group of Imperial Inquisitors arrive to destroy the newly rising Jedi.\\

\textbf{Exploring Moraband:} For GMs who have seen Star Wars: Rebels\texttrademark they should be aware of how to describe Moraband.  If not when the PJs enter the Sith Graveyard the graveyard is not tombstones.  Think more the charged blackened husks of bodies similar to what one would see in Pompeii with ancient lightsabers sprinkled about that are not it working condition.\\


\subsection{Récompenses de la chasse aux fantômes}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{4cm}|p{12cm}|}
	\hline 
	\cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Élement de l'histoire}}} & \cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Récompense}}} \\ 
	\hline 
	Effort de récupération au Sanctuaire Jedi sur la lune de Delriss. & Les PJ ont-ils pu récupérer quelque chose de la bibliothèque sur la lune d'eau du système Delriss ? 
	\begin{itemize}
		\item \textbf{Histoire du Temple Jedi par un étudiant} (Une carte du Temple Jedi sur Coruscant),
		\item \textbf{Registre de la perte des mémoires du conflit séparatiste} (Ajouter un Boost sur les test de Connaissances (guerre)),
		\item \textbf{Les spécifications techniques complètes pour le Delta-7 Aethersprite Class Light Interceptor} (Ouvrez la possibilité de créer un vaisseau de combat),
		\item \textbf{Une série de réflexions et de poésie sans titre de l'obscur philosophe Jedi Kelin Dass} (Réduit le coût de la puissance de base de la puissance de 1 force par 5),
		\item \textbf{Les réflexions sur la Forme III Démêler la contradiction de la Puissance et de la Protection par le Chevalier Jedi Aurilan} (Donne la compétence de sabre laser comme compétence de carrière)
		\item \textbf{Droïde Astromech} (Si la réparation est réussie, vous pouvez l'ajouter comme récompense d'équipement)
		\item \textbf{Delta 7 Aethersprite Interceptor} (Si la réparation est réussie, vous pouvez l'ajouter comme récompense d'équipement)
	\end{itemize}
	\\ 
	\hline 
	Affecté par le côté obscur. & Les événements de Moraband devraient avoir un impact considérable sur les PJ. Le MJ devrait ajouter quelque chose dans le journal d'aventure de chacun sur ce qu'il a rencontré sur Moraband, comment cela l'a affecté, et quels types de cauchemars ou de problèmes le PJ rencontrera en fonction des effets durables de son voyage sur la planète Sith. \\ 
	\hline 
	Le destin de Suljo Warde. & Quel a été le sort de Suljo Warde ?  Les PJs l'ont-ils tué, les PJs lui ont-ils permis de survivre là où il devient un ennemi du parti ?  Les PJs l'ont-ils racheté et ramené du Côté Lumineux où il retourne avec eux au Temple de l'Aurore pour devenir professeur ? \\ 
	\hline 
\end{tabular} 

\subsection{Récompenses d'XP}
\begin{tabular}{|p{12cm}|p{4cm}|}
	\hline 
	\cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{XP}}} & \cellcolor{DarkRed} {\large \textcolor{PureWhite}{\textbf{Récompense}}} \\ 
	\hline 
	Récupérer les coordonnées de Moraband dans le sanctuaire perdu des Jedi. & 5 XP \\ 
	\hline 
	Eviter ou vaincre les ennemis qui ont poursuivi les PJs jusqu'à Moraband. & 10 XP \\ 
	\hline 
	Surmonter les défis dans la section Secrets de Moraband. & 1 -- 5 XP \\
	\hline 
	Vaincre Suljo Warde au combat. & 10 XP \\
	\hline 
	Briser l'emprise du côté obscur de Warde. & 20 XP \\
	\hline 
	Obtaining the final kyber crystal. & 10 XP \\
	\hline 
	Bon jeu de rôle (jouer en fonction des obligations, des devoirs, de la moralité et des motivations du personnage) & 1 -- 5 XP \\
	\hline 
\end{tabular}


\end{document}
