\documentclass{article}
\usepackage[french]{babel}
\usepackage[T1]{fontenc}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{Encounter Ideas}
\usepackage{multicol}

\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
%\setmainfont[Mapping=tex-text]{Sitka Display}
\usepackage[small,sf,bf]{titlesec}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{sectsty}

\definecolor{DarkGreen}{HTML}{384d3e}
\definecolor{PureWhite}{HTML}{FFFFFF}
\definecolor{DarkRed}{HTML}{6e272d}
\definecolor{DarkGold}{HTML}{a48e3b}

\sectionfont{\color{DarkGreen}}
\subsectionfont{\color{DarkRed}}
\subsubsectionfont{\color{DarkGold}}

\begin{document}

\title{\vspace{-0.5cm}{\Huge Encounter Ideas} \vspace{-1cm}}

\date{}

\maketitle

\section*{1 --- 20 : Urban}
\begin{enumerate}
	\item A Rodian bounty hunter passes by. He looks you over and assesses you quickly before continuing on.
	\item A near-Human bumps into you and quickly excuses himself. You hear others in the area murmuring about that being the individual a Defel assassin is looking for.
	\item A well-dressed Devaronian approaches you and asks directions to the nearest weapon shop.
	\item A large group of Duros wearing uniforms leave a restaurant. They get inside of a land speeder and depart the area heading towards the nearest starship docking area.
	\item A group of local law enforcement are being led by a Gotal tracker. They enter into the building that you are about to go into. As you approach the front of the building, two of the law enforcement officers standing outside tell you that the building is now closed and you’ll have to come back later.
	\item A hover barge slowly travels down the street. It contains a raucous crowd that appears heavily armed, all centered around a large Hutt. The Gamorrean bodyguards stare you down as the barge passes by you.
	\item An Imperial hover transport passes by you. It has the markings of a prisoner or slave transport ship. You hear what sounds like a loud scream come from the inside of the transport and then silence. From the rear-view window you see at least a dozen Jenets in gray uniforms and full restraints seated inside.
	\item An Ortolan sitting at the base of a building asks you if you have any spare change.
	\item A squad of Storm Troopers approach you and demand to see your identification.
	\item A human foreman leads a small group of Ossans in the construction of a building next to the building you are entering. A large piece of framework falls onto one of the Ossans, injuring him and pinning him to the ground.
	\item Medics are attending to several individuals in a land speeder accident involving three vehicles. Two of the victims involved are clearly deceased. An argument is starting to ensue between several people involved in the accident and other individuals in the area. There is no law enforcement on scene yet.
	\item A female Togorian stares at a monument located in a central square. She snarls at you as you pass by.
	\item Your vehicle sputters to a stop in the middle of the road. A Verpine tinkerer that happens to be conveniently in the area approaches you and offers to fix your vehicle for you. This must be a setup…
	\item A swoop gang buzzes through the streets at a high rate of speed on their Nebulon-Q Swoops. Shortly afterwards, you see local law enforcement speeding in the same direction.
	\item A Whiphid passes by you riding a very large, lizard-like creature. You’re pretty sure that neither are native to this planet and they both look extremely out of place. The people in the area give them a wide berth.
	\item An armed group of Humans lead a shackled Abyssin down a side alley. You observe them knock on a door and then they all enter the building.
	\item An Aqualish is surrounded by several Storm Troopers and arguing with them on a street corner. The Aqualish makes a furtive movement towards his waistband as two Storm Troopers shoot him dead. The Storm Troopers start highly encouraging bystanders to move along.
	\item An Arcona tradesman stands near an open vehicle on a street corner. As you pass by he asks if there are any particular items you are looking for that he could help with. When you approach, he moves a velvet cloth covering a square black box, approximately half a cubic meter in size. The box looks oddly familiar to you.
	\item An Imperial transport slowly hovers past you. As it enters an open intersection, the vehicle erupts into a violent explosion sending shrapnel everywhere. Most of the bystanders nearby start running for cover, albeit far too late. A Bothan bumps past you with a grin on his face and mutters something under his breath.
	\item Two Mon Calamari and a Human approach you. The Human nods at you and waits, as if you are going to do something. After several seconds, he looks at you and states, "Are we just going to stand here or are we going to do this?"
\end{enumerate}

\section*{21 --- 40 : Space}
\begin{enumerate}
	\setcounter{enumi}{20}
	\item A small space station looms in the area that you are passing through. It looks scientific in nature, possibly an observation post. There is power to the facility but no apparent movement or life signs currently on board.
	\item Your starship’s sensors pick up another starship’s emergency beacon for a short amount of time. Before you can narrow down an exact location, the beacon goes silent.
	\item You are forced to navigate around a large field of space debris. The debris appears to be from old cargo hauler, possibly a Mobquet Medium Cargo Hauler. The wreckage appears to be fairly recent.
	\item A squad of TIE Fighters are chasing after a Starlight Light Freighter. The two lead TIE Fighters fire several shots, disabling the engines of the freighter. A transmission is sent to your ship warning you to leave the area and not interfere.
	\item A line of six Zuraco Cargo Haulers slowly pass by you at sublight speed heading towards the nearest planet.
	\item An Imperial Interdictor Cruiser looms before you. You see a SoroSuub Luxury Cruiser 200 hovering near the Interdictor Cruiser. An Imperial Gamma-Class Assault Shuttle appears to be docking with the luxury yacht as a squadron of TIE Fighters circle the area.
	\item An Imperial Customs Frigate notifies you of its intention to search your vessel. It orders you to stop your ship, power down, and prepare to be boarded.
	\item A heavily modified Imperial Custom Frigate speeds towards your ship. An alien voice comes over your communication channel telling you that the Nikto Kajidic is taking control of your ship. You recall that name being associated with a pirate ship that has been patrolling the area.
	\item An Imperial System Patrol Craft cruises through the area at a high rate of speed. Your sensors detect that it scans your vessel for a short amount of time before it continues past you.
	\item A Trianii Ranger Patrol force parallels your ship’s trajectory. The force includes six RX4 Patrol Ships. After mirroring your flight path towards your destination for approximately a minute, the force veers off and heads away from you.
	\item A local, intra-system IR-3F Patrol Ship appears to be heading back towards the nearest planet. You can see a moderate amount of damage on the exterior of the hull. The three remaining Turbolaser turrets are actively scanning the area.
	\item An Aavman Extravagance 11-S Space Yacht passes by your ship. It is being escorted by two Toscan 8-Q Starfighters.
	\item A large amount of space debris from a nearby asteroid field is causing a disturbance with your ship’s sensors. In order to travel into hyperspace, you’re going to have to navigate around the debris which will take approximately thirty minutes. During that time, your ship’s sensors will most likely not operate properly.
	\item A large group of Y-TIE Ugly Starfighters appear to be headed in your direction. They haven’t attempted to communicate with your ship yet, but you know the ships are most often associated with mercenaries and petty crime lords. It doesn’t look good…
	\item You observe a small object floating off the starboard side of your ship. Quick observation of the object reveals it to be an Armored Spacesuit (Merr-Sonn Weapons Superior Boarding Armor). It appears to be drifting through space slowly. A sensors check of the suit reveals the individual inside the suit is…
	\item A heavily modified HT-2200 Medium Freighter appears to be mining a local asteroid belt. The underbelly cannon has been replaced with a large mining tool. To your knowledge, mining this part of the asteroid belt is illegal.
	\item A squad of TIE Fighters enter your ship’s area. They request that you identify yourself and your destination.
	\item You spot a Victory Class Star Destroyer looming in the distance. The transponder code identifies it as the Basilisk II. Two TIE Fighter squadrons swarm around it and you can see several other starships in the area. Your ship’s sensors detect that it is attempting to scan your ship from long range.
	\item A gravity disturbance begins rocking you ship. Emergency lights begin to blare and you can hear a small explosion shutter the back of your ship. Just as quickly as it began, the disturbance stops. You better check to see what kind of damage your ship has suffered. You glance out of your cockpit as you move to check your ship. Is that another ship headed towards you…?
	\item A large space station can be seen in the distance. Small intra-planetary ships can be seen traveling to and from it. A communication from the station appears on your command screen. It appears to be some sort of announcement, but it is in a language that you are not familiar with.
\end{enumerate}

\section*{41 --- 60 : Wilderness}
\begin{enumerate}
	\setcounter{enumi}{40}
	\item A large group of predatory birds circle over head. Either something just died in the area, or something is about to.
	\item Mechanical stomps and grinding can be heard in the distance. An AT-ST stomps by you, unaware that you are in the area. The vehicle has damage to the driver-side knee joint. The drive engine whirs and grinds uncontrollably loud. There is a large amount of carbon scoring on the cockpit.
	\item Howling can be heard in the distance. Then, more howling from a different direction, as if in response to the first. At that point, you notice a faint trail leading through this area. A large animal carcass sits off to the side of the trail. This can’t be good…
	\item You come upon an area that has an encrusted, spherical growth approximately one hundred meters in diameter emanating from the ground. There are several large holes that appear to be entrance tunnels into the growth that go deeper into the ground. You can hear a large buzzing sound coming out of the holes. The longer you listen, the louder the buzzing seems to be getting.
	\item A small group of near-humans riding what appear to be beasts of burden slowly pass by you. Their clothing, weapons, and technology strike you as very primitive, possibly natives of this planet. They seem utterly unconcerned by you presence.
	\item You hear blaster fire in the area and what sounds like the cries of a large animal. From a distance away, you locate a speeder containing three Humans near a large animal that is indigenous to the area. You aren’t completely sure, but they appear to be poachers.
	\item The ground beneath your feet begins to quake. A fissure cracks in front of you and steam begins to bellow out. The temperature in the air appears to be rising rapidly. You are finding it difficult to breath. Did you remember to bring a respirator?
	\item You come upon an area that contains a large radar dish pointed up towards the sky. There are numerous boxes dotting the area that are connected to the dish. It appears to be some sort of data gathering device.
	\item You discover a wide-open field. The area appears to have been professionally leveled and cleared of debris. It looks like it may be a landing area for small or medium sized starships. It looks like it was used very recently.
	\item You discover the wreckage of a large starfighter, approximately seventy meters in length. Upon further inspection, it appears to be an old Star Cab exploration vessel. Judging by the plant growth around the vessel, it appears to have been here for a very long time, possibly decades.
	\item You stumble upon an incredibly large pit, approximately one mile in diameter. You see numerous different species using various equipment to mine resources from the pit. Several "pit bosses" appear to be directing the work inside the pit. You see one Human in an Imperial officer’s uniform that appears to be overseeing the work.
	\item You discover what appears to be an archeological expedition’s camp site. It does not appear that anyone has been here for several days.
	\item You discover a solitary farm out in the middle of no where. The area appears almost unnaturally located in this area. A lone Ithorian farmer plows his crop on a hovering tractor.
	\item While walking through a remote area, you stumble across a strange building carved into the side of a large rock face. It has unique glyphs that appear to be some sort of star chart carved on the outside. It appears to be a crypt for a family of Duros.
	\item Three Gotals on heavily modified Swoops races past you. You can’t tell if they are chasing something, or running away from something.
	\item You locate an old abandoned Imperial supply depot. It appears to have been out of use for a long time. It looks like the supplies were removed from the depot or it has been looted recently. It also looks like something very large is currently living inside.
	\item You encounter a strange Ubese hermit and his horde of droids. He claims that you are on his mining plot and must leave. Unfortunately, this is really close to the destination you were heading to.
	\item You run into a band of Human slavers loading up several natives into a transport vehicle. It appears that the slavers have already killed several of the natives. If they notice you, you might be next.
	\item A large herd of native herbivores can be seen grazing in the distance. A blaster shot rings out and they begin to stampede in your direction.
	\item You discover a mobile Imperial base. It appears that it has been deployed in the area for several days. You detect at least four dozen Imperial personnel in the area with support vehicles. They seem oblivious to your presence.
\end{enumerate}

\section*{61 --- 70 : Urban}
\begin{enumerate}
	\setcounter{enumi}{60}
	\item A droid wheels up to you and catches your attention. It directs you towards a heavily armed and armored Gand across the street from you. The Gand appears to be a bounty hunter. The droid tells you that the individual is looking for you.
	\item A Quarren approaches you and begins muttering something in his native tongue. After several moments, he falls dead at your feet. Local law enforcement rounds a corner and appears to be briskly walking towards you.
	\item A Shistavanen tracker leads a group of rough-looking Humans towards local drinking establishment. They line up outside the building and unleash a hail of blaster fire into the business. Moments later, the Shistavanen takes off in one direction and the Humans in another direction.
	\item A Sullustan approaches you on a street corner. He offers to fix your equipment, droids, or starship for a huge discount.
	\item A Teltior gambler offers you a seat at his sabacc table. Only a buy-in of one hundred credits. The other individuals at that table seem… welcoming…
	\item A Bimm tradesman approaches you and states that he has numerous artifacts for trade. He invites you over to his shop because he believes that he has something of interest for you.
	\item Two Devaronians and a Chiss walk into a bar. The first Devaronian asks the Chiss what is wrong. The Chiss responds, saying that he is feeling a little sad. The second Devaronian states, "Oh, so you’re feeling blue?" The Chiss shoots both Devaronians dead and leaves.
	\item A Falleen noble and his entourage are proceeding through town, they stop to ask you where the most prominent hotel is in the area. Before you can respond, one of the Falleen suggests that instead of telling them where it is, you come with them and show them. You feel strangely compelled to help them.
	\item A Klatooninian approaches you and states that his Hutt master wishes to speak with you. He won’t take no for an answer.
	\item A malfunctioning astrogation droid buzzes into the area and begins firing a small blaster pistol. Shortly afterwards, the droid explodes in a hail of shrapnel. Was it truly malfunctioning, or was it a terrorist attack?
\end{enumerate}

\section*{71 --- 80 : Space}
\begin{enumerate}
	\setcounter{enumi}{70}
	\item You detect a weak signal from a starship’s emergency beacon on the edge of an asteroid belt. When you go to investigate, a heavily modified SoroSuub Nesst-class Light Freighter blasts out of the asteroid belt headed in your direction. It’s a trap!
	\item Something is causing a blackout with all communication devices in the nearby area. It is difficult to determine whether this is a natural phenomenon or if something is actively causing the disruption.
	\item A large Nalroni merchant fleet appears to be readying for a jump to light speed. As the entire fleet enters into hyperspace travel, a lone Action IV Bulk Freighter is left behind, apparently having navigation difficulties. The medium bulk freighter appears defenseless due to the fact that it has no external weapons.
	\item A Dynamic-Class Freighter drifting through space sends a communication to your starship. It states that it has run out of fuel. In exchange for part of your fuel, they will offer you detailed knowledge for your star chart relating to this system.
	\item You find an Imperial probe droid floating near an interstellar navigational beacon. It appears to be in good condition but is not operating. Probes like this are very valuable and contain a vast amount of data, but collecting them is against Imperial law and punishable by death.
	\item You come upon a TL-1800 Transport freighter that appears to be traveling very slowly. It does not appear damaged, but is traveling in a large circle. Sensors reveal that there are no life signs on board. The starship appears to be in good condition. It also appears that are an excessive amount of droids on the ship.
	\item Your starship encounters a lightning storm while traveling through the atmosphere of a planet. Bolts of lightning course through the exterior of the ship. You are unsure if any damage occurred, but you should definitely check when you get a chance.
	\item A spherical probe is moving on a linear path towards you. As it approaches, you detect that its sensors are heavily scanning your starship.
	\item A large, organic creature floats by your ship. You’ve never seen anything like it. You should probably steer clear of it since it appears large enough to swallow your ship whole.
	\item While attempting to enter planetary orbit, you are informed by space traffic control that only authorized vessels are being allowed entrance into the starport. They refuse to give a reason for their decision.
\end{enumerate}

\section*{81 --- 90 : Strange}
\begin{enumerate}
	\setcounter{enumi}{80}
	\item You and your friends wake up in an unfamiliar room, weak, disoriented and partially blind. One of you realizes and tells the rest of the group that you seem to be suffering the effects of hibernation sickness. You discover several opened carbonite transportation blocks in the room with you.
	\item You discover a small cube in the cargo area of your ship. Whenever you try to get close enough to inspect it, you become extremely dizzy and begin to faint.
	\item You encounter a small space station in an odd location. You are absolutely sure there is not supposed to be one located here. The station appears to have no means of relocating itself. There does appear to be life signs on the station, but there is no response to any attempts at communication.
	\item You meet a droid that claims to be able to manipulate the Force.
	\item The last thing you remember is plotting coordinates to land your starship on your destination planet. You and your crew awoke to find your ship traveling in hyperspace to an unknown destination.
	\item You discover a starship that looks exactly like your ship. In fact, it is your ship minus the fact that it is heavily damaged. It looks like your ship, but from the future. Records on the ship indicate that whatever happened will happen within the next few days.
	\item You stumble upon what appears to be a void in space. Sensors readings offer no information of note. There is a strong gravitational pull towards the area. Perhaps it is a black hole?
	\item You locate a cryogenically frozen body inside a transport container. The outline of the individual looks incredibly like you. In fact, such a dead-on replica of you, it is eerie…
	\item Your ship is traveling through space as you come upon a small starship with a very unusual design. Although you can visually see it, the ship does not register on your sensors. As you approach it, your sensors detect a small anomaly right before the ship vanishes from sight.
	\item You discover a Human slumped over in the cockpit of a landspeeder. As you approach, you notice that he is unconscious, holding a blaster pistol in one hand a clutching a piece of paper in another. The paper falls to the ground. You discover that it is a wanted poster… of you.
\end{enumerate}

\section*{91 --- 101 : Force}
\begin{enumerate}
	\setcounter{enumi}{90}
	\item You stumble upon a dead Twi’lek at the entrance to an alley. From your estimates, he most likely died recently. You’re not sure, but it looks like he was killed by a lightsaber.
	\item A near-Human street urchin calls you over to his sales cart. He checks the surrounding area before he shows you what he claims to be his most prized possession. He then presents to you an item that he claims to be a Jedi Holocron. It could be all yours, for the right price.
	\item A Human dressed in dark robes approaches you and asks you who you are. For some reason, you blurt out the answer. He then orders you to follow him into a building. For some reason, you feel compelled to put your weapons on the ground and follow him.
	\item You feel a disturbance in the force, even though you are not force sensitive…
	\item Upon entering a building, a near-Human walks up to you and states that you’re not welcomed here. He swipes part of his trench coat back to reveal a lightsaber on his hip. There appear to be several other individuals standing behind him that are backing him up.
	\item A vehicle careens off the roadway and towards a group of bystanders. One of the individuals raises his hands and the vehicle hovers to a stop right in front of him. As the vehicle slowly drops to the ground, the individual disappears down an alleyway.
	\item Inside a cargo container, you discover a unique, portable hibernation pod. You see a strange alien that appears to be frozen in stasis. It clutches a lightsaber to its chest with both hands. The markings on the outside of the container are foreign to you. The best you can make out is that it appears to state, "Do not open."
	\item A Tarasin approaches you. He tells you that the Force led him to you and that you are in grave danger. Moments later, you hear blaster fire and screams coming from behind a nearby building. He looks back and you and states, "We must go. There isn’t much time."
	\item While drinking at a bar, a highly intoxicated Human whispers to you that he was once the greatest Jedi in the Galaxy. Without waiting for your response, he tells you he’ll prove it. He quietly peers across the bar and points his finger at a bottle of liquor on a shelf. The bottle shakes a little, falls to the ground and shatters. As the bartender cleans the mess up, the Human looks back at you, winks, and takes a sip of his drink.
	\item A duel erupts in the middle of a busy square between two Jedi. As their lightsaber battle ensues, many bystanders run in the opposite direction while some stare in awe at the sight.
	\item A Zabrak approaches you and stops a medium distance away. He slowly draws a lightsaber from his waistband and ignites it. His other hand crackles with electricity.
\end{enumerate}

\end{document}
